### 2018-05-01 General WLD combinatorics.tex
some typos and comments in sections 1, 2.1 and 2.2

We depict this data as a convex polygon, with vertices labeled by $V$ (preserving the cyclic ordering), and $k$ wavy lines in the interior of the diagrams. The pair $p_r$ defines a wavy line from the $i_r^{th}$ edge (between $i_r$ and $i_r+1$) and the $j_r^{th}$ edge. These are called propagators.  The condition on $i_r$ and $j_r$ means that the propagator does not go between adjascent edges. Let $\cP = \{p_r\}_{r=1}^k$ be the set of propagators. Then we write \bas W = (\cP, V) \;.\eas

@@

\begin{dfn} \label{VPropdfn}
Let $W = (\cP, n)$.
\begin{enumerate}
\item For $p \in \cP$, let $V_p = \{i_p, i_p+1, j_r, j_r+1\}$ be the set of vertices supporting $p$. Then, for $P \subset \cP$, the set $V_P = \cup_{p \in P} V_p$ is the vertex support of $P$.
\item For $V \subset [n]$, write $\Prop(V) = \{ p \in \cP | V_p \cap V \neq \emptyset \} $.
\end{enumerate}
\end{dfn}

@@

\begin{dfn} \label{subdiagramdfn}
Let $W = (\cP, n)$ be an admissible Wilson loop diagram. A subdiagram of $W$ is defined by a a subset of propagators of $W$. For $P \subset \cP$, write $W|_P = (P, V(P))$.
\end{dfn}

@@

\begin{dfn}\label{equivdfn}
There is an equivalence relationship on the set of admissible Wilson loops diagrams: $W = (\cP, n)$ and $W'= (\cP', n)$ are equivalent if
\begin{enumerate}
\item There exist two different exact subdiagrams, $(P, V(P))$ and $(P', V(P'))$ of $W$ and $W'$ respectively such that $V(P) =  V(P')$.
\item The complementary subdiagrams are identical: $(\cP \setminus P, V(P)^c) = (\cP' \setminus P', V(P')^c)$.
\end{enumerate}
\end{dfn}

@@

In \cite{wilsonloop}, Amat and Agarwala show that admissible Wilson loop diagrams with $k$ propagators corresponds to positroids of rank $k$ (a matroid that can be represented by an element of $\Gr(k, n)$. )

\begin{thm}\cite{wilsonloop}An admissible Wilson loop diagram, $W =(\cP, n)$, defines a matroid with base set $[n]$. The independent sets are exactly those subsets $V \subseteq [n]$ such that $\not \exists U\subseteq V$ satisfying $|\Prop(U)|> |U|$. \label{thm:WLDmatroid}\end{thm}

This does not, however, show that the matroids associated to each Wilson loop diagram is unique. In fact, in \cite{wilsonloop}, the authors show that if two diagrams are equivalent then they define the same matroid [cite theorem here].

@@

\begin{dfn} For a Wilson Loop diagram $W = (\cP, [n])$, the associated matroid $M(W)$ can be defined by any of the following sets of subsets
\begin{enumerate}
\item A basis of $W$ is any independent set, $B \subset [n]$ of size $|B| = |\cP|$.
\item The rank of a set $|V| \subset [n]$, is bounded above by $\rk(V) \leq \min\{ |V| , |\Prop(V)|\}$. If $V$ is an independent set, then $\rk(V) = |V|$. Furthermore, if $v \in [n]$, and $q \in \Prop(v)$, then for any $V \subset [n]$ such that $q \not \in \Prop(V)$, $\rk(V \cup v) = \rk(V) +1$. That is, adding a vertex that supports a new propagator to a set increases the rank of the set.
\item A circuit of a matroid is any set $C \subset [n]$ such that every proper subset $U \subsetneq C$ is independent. That is, $\rk(C) = |C|-1$. The union of circuits is called a cycle. If $C$ is a circuit of an admissible Wilson loop diagram, and $e \in C$, \bas |\Prop(C\setminus e))| \leq |C\setminus e| = \rk(C) \leq \min\{|C|, |\Prop(C\setminus e)|\}\;.\eas
    In other words, if $C$ is a circuit of a Wilson loop diagram, then \bas \rk(C) = |C|-1 = |\Prop(C)| \;. \eas
\item A flat, $F$, of a matroid is a maximally dependent set. That is, for all $e \not \in F$ $\rk(F \cup e) = \rk(F) +1$. If $W$ is an admissible Wilson loop diagram, any group of propagators defines a flat, $F(P) = V(P^c)^c$, called a propagator flat. It consists of all vertices of $W$ that do not support any propagators outside of $P \subset \cP$. To see that this is flat, let $v \in V(P^c)$. We have that there is a $q \not \in P$ such that $q \in \Prop(v)$. Therefore, by the rank function, $\rk( F(P) \cup v))> \rk(F(P))$.
\end{enumerate}
\end{dfn}

@@

\begin{cor} \label{classifyflats}
If $F$ is a flat of a Wilson loop diagram, it can be written as the union of a cyclic flat, and thus a propagator flat, and an independent flat.
\end{cor}
From this we see that any propagator flat can be written as a union of a cyclic propagator flat and an independent flat.

@@

Since the matroids defined by the subdiagram $(P , V(P)$ is not the same as the matroid associated to $W_{V(P)}$, one cannot say that the $W_{V(P)}$ is a uniform matroid. Infact, for any subset $U \subset V(P)$, $\rk_{W_{V(P)}}(U) \geq \rk_{(P , V(P)}(U)$. This is because adding propagators to vertices can only increase the rank. In particular this implies that, for any subset $U \subset V(P)$, if $|U| \leq |P|$, then $U$ is independent in both the restricted matroid $W_{V(P)}$, and the original, $W$.

@@

\begin{lem} \label{maxexactcomplementrank}
Let $W = (\cP, [n])$ be a Wilson loop diagram, and $(P, V(P))$ an exact subdiagram with $P \subsetneq \cP$. Then the set $V(P)^c = F(P^c)$ is a propagator flat of maximal rank  \bas \rk F(P^c) = |P^c| \;. \eas If $(P, V(P))$ is maximal, then $F(P^c)$ is cyclic.
\end{lem}

@@

Let $(Q, V(Q))$ be an exact subdiagram that is not maximal, with $Q \subset P$ defining he maximal exact subdiagram above. Then by lemma \ref{??} $|V(P)| = |V(Q)| + |P \setminus Q|$. Let $F(P^c)$ be the cyclic set defined as the complement of $V(P)$. Then $V(Q)^c = F(P^c) \cup F$, where $F$ is an independent set of size $|P \setminus Q|$ and with $(P \setminus Q) \subset \Prop (F)$. Thereofore, $\rk (F) = |Q^c|$. 
\end{proof}

@@

\begin{thm}
Let $W= (\cP, [n])$ and $W'= (\cP', [n])$ be two Wilson Loop diagrams. They define the same matroid if and only if $W \sim W'$.
\end{thm}

>>>>

We depict this data as a convex polygon, with vertices labeled by $V$ (preserving the cyclic ordering), and $k$ wavy lines in the interior of the diagrams. The pair $p_r$ defines a wavy line from the $i_r^{th}$ edge (between $i_r$ and $i_r+1$) and the $j_r^{th}$ edge. These are called propagators.  The condition on $i_r$ and $j_r$ means that the propagator does not go between adjacent edges. Let $\cP = \{p_r\}_{r=1}^k$ be the set of propagators. Then we write \bas W = (\cP, V) \;.\eas

@@

\begin{dfn} \label{VPropdfn}
Let $W = (\cP, n)$.
\begin{enumerate}
\item For $p \in \cP$, let $V_p = \{i_p, i_p+1, j_r, j_r+1\}$\note{This has a notational problem, should $p$ be the subscript or $r$.  I think $p$ is better and is entirely clear, but strictly speaking that's not what Definition~\ref{WLdfn} says (though in this case since we don't know the index of $p$ we don't have any way to write $p$'s ends by a strict interpretation of Definition~\ref{WLdfn}).} be the set of vertices supporting $p$. Then, for $P \subset \cP$, the set $V_P = \cup_{p \in P} V_p$ is the vertex support of $P$.\note{I don't like using $\subset$ in a mixed audience because whether or not $\subset$ is strict depends on whether you are an algebraic geometer (and some other related areas) or not so in a mixed audience it is unclear.}
\item For $V \subset [n]$, write $\Prop(V) = \{ p \in \cP | V_p \cap V \neq \emptyset \} $.
\end{enumerate}
\end{dfn}

@@

\begin{dfn} \label{subdiagramdfn}
Let $W = (\cP, n)$ be an admissible Wilson loop diagram. A subdiagram of $W$ is defined by a a subset of propagators of $W$. For $P \subset \cP$, write $W|_P = (P, V(P))$.
\end{dfn}
\note{Later I will also want a different kind of subobject, one with a subset of the propagators but where the vertex set contains $V(P)$ but may be larger (the most important instance being when it is $[n]$.)  This kind of subobject doesn't need a particular name, nor does it need to be defined up here, but I wanted to mention it so we have it in mind.}

@@

\begin{dfn}\label{equivdfn}\note{Maybe it would be clearer to say the equivalence relation generated by $W$ and $W'$ which satisfy $1$ and $2$; this helps the note in the next example be less awkward too.}
There is an equivalence relationship on the set of admissible Wilson loops diagrams: $W = (\cP, n)$ and $W'= (\cP', n)$ are equivalent if
\begin{enumerate}
\item There exist two different exact subdiagrams, $(P, V(P))$ and $(P', V(P'))$ of $W$ and $W'$ respectively such that $V(P) =  V(P')$.
\item The complementary subdiagrams are identical: $(\cP \setminus P, V(P)^c) = (\cP' \setminus P', V(P')^c)$.
\end{enumerate}
\end{dfn}

@@

In \cite{wilsonloop}, Amat and Agarwala show that admissible Wilson loop diagrams with $k$ propagators corresponds to positroids of rank $k$ (a matroid that can be represented by an element of $\Gr(k, n)$.)

\begin{thm}[\cite{wilsonloop}] An admissible Wilson loop diagram, $W =(\cP, n)$, defines a matroid with base set $[n]$. The independent sets are exactly those subsets $V \subseteq [n]$ such that $\not \exists U\subseteq V$ satisfying $|\Prop(U)|> |U|$. \label{thm:WLDmatroid}\end{thm}

This does not, however, show that the matroid associated to each Wilson loop diagram is unique. In fact, in \cite{wilsonloop}, the authors show that if two diagrams are equivalent then they define the same matroid [cite theorem here].

@@

\begin{dfn} For a Wilson Loop diagram $W = (\cP, [n])$, the associated matroid $M(W)$ can be defined by any of the following sets of subsets
\begin{enumerate}
\item A basis of $W$ is any independent set, $B \subset [n]$ of size $|B| = |\cP|$.
\item The rank of a set $|V| \subset [n]$, is bounded above by $\rk(V) \leq \min\{ |V| , |\Prop(V)|\}$. If $V$ is an independent set, then $\rk(V) = |V|$\note{The spacing is weird in $\rk$.  Looking at your definition I think it is on purpose, so I think I'm missing something as to why.  It looks particularly odd when there is a subscript to the rank eg after Def 2.10}. Furthermore, if $v \in [n]$, and $q \in \Prop(v)$, then for any $V \subset [n]$ such that $q \not \in \Prop(V)$, $\rk(V \cup v) = \rk(V) +1$. That is, adding a vertex that supports a new propagator to a set increases the rank of the set.
\item A circuit of a matroid is any set $C \subset [n]$ such that every proper subset $U \subsetneq C$ is independent. That is, $\rk(C) = |C|-1$. The union of circuits is called a cycle. If $C$ is a circuit of an admissible Wilson loop diagram, and $e \in C$, \bas |\Prop(C\setminus e))| \leq |C\setminus e| = \rk(C) \leq \min\{|C|, |\Prop(C\setminus e)|\}\;.\eas
    In other words, if $C$ is a circuit of a Wilson loop diagram, then \bas \rk(C) = |C|-1 = |\Prop(C)| \;. \eas
\item A flat, $F$, of a matroid is a maximally dependent set \note{Maximal for its rank is better than maximally dependent.  Alternately maybe maximal for dependence would be better, but in that case I would really just be meaning rank again}. That is, for all $e \not \in F$ $\rk(F \cup e) = \rk(F) +1$. If $W$ is an admissible Wilson loop diagram, any group of propagators defines a flat, $F(P) = V(P^c)^c$, called a propagator flat. It consists of all vertices of $W$ that do not support any propagators outside of $P \subset \cP$. To see that this is flat, let $v \in V(P^c)$. We have that there is a $q \not \in P$ such that $q \in \Prop(v)$. Therefore, by the rank function, $\rk( F(P) \cup v))> \rk(F(P))$.
\end{enumerate}
\end{dfn}

@@

\begin{cor} \label{classifyflats}
If $F$ is a flat of a Wilson loop diagram, it can be written as the union of a cyclic flat, and thus a propagator flat, and an independent flat.\note{What would you think of putting ``and thus a propagator flat'' in parentheses or something; otherwise I'm concerned that the nesting structure of this sentence is not sufficiently clear.}
\end{cor}
From this we see that any propagator flat can be written as a union of a cyclic propagator flat and an independent flat.

@@

Since the matroid defined by the subdiagram $(P , V(P))$ is not the same as the matroid associated to $W_{V(P)}$, one cannot say that the $W_{V(P)}$ is a uniform matroid. In fact, for any subset $U \subset V(P)$, $\rk_{W_{V(P)}}(U) \geq \rk_{(P , V(P))}(U)$. This is because adding propagators to vertices can only increase the rank. In particular this implies that, for any subset $U \subset V(P)$, if $|U| \leq |P|$, then $U$ is independent in both the restricted matroid $W_{V(P)}$, and the original, $W$.

@@

\begin{lem} \label{maxexactcomplementrank}
Let $W = (\cP, n)$ be a Wilson loop diagram, and $(P, V(P))$ an exact subdiagram with $P \subsetneq \cP$. Then the set $V(P)^c = F(P^c)$ is a propagator flat of maximal rank  \bas \rk F(P^c) = |P^c| \;. \eas If $(P, V(P))$ is maximal, then $F(P^c)$ is cyclic.
\end{lem}

@@

Let $(Q, V(Q))$ be an exact subdiagram that is not maximal, with $Q \subset P$ defining he maximal exact subdiagram above. Then by lemma \ref{??} $|V(P)| = |V(Q)| + |P \setminus Q|$. Let $F(P^c)$ be the cyclic set defined as the complement of $V(P)$. Then $V(Q)^c = F(P^c) \cup F$, where $F$ is an independent set of size $|P \setminus Q|$ and with $(P \setminus Q) \subset \Prop (F)$. Therefore, $\rk (F) = |Q^c|$. 
\end{proof}

@@

\begin{thm}
Let $W= (\cP, [n])$ and $W'= (\cP', [n])$ be two Wilson Loop diagrams. They define the same matroid if and only if $W \sim W'$.
\end{thm}
\note{I don't understand how this section (and this theorem) relate to the preivous section, which has the same content in its main theorem.}
